Distributed Version Control Systems

### 2010-04-27 paper.tex
Agregue otra sección a "Should I use it in my project?"

\newcommand{\latexiie}{\LaTeX2{\Large$_\varepsilon$}}

%\usepackage{ieeetsp}	% if you want the "trans. sig. pro." style
%\usepackage{ieeetc}	% if you want the "trans. comp." style
%\usepackage{ieeeimtc}	% if you want the IMTC conference style

@@

>>>>

\newcommand{\latexiie}{\LaTeX2{\Large$_\varepsilon$}}
\usepackage{graphicx}
%\usepackage{ieeetsp}	% if you want the "trans. sig. pro." style
%\usepackage{ieeetc}	% if you want the "trans. comp." style
%\usepackage{ieeeimtc}	% if you want the IMTC conference style

@@

\subsection{Independent subteams}
If the application being developed requires a large amount of people working at the same time, it is very likely that they are working on different subsystems. Each subteam can be working on a different repository, and so the chances of one team messing with the other teams build is completely removed. This helps each team to mantain their own build and if a problem on the build arises, then it is something to be solved between a reduced group of people.

Then both repositories can be merged togheter into an integration one by pulling from each of them. If there are conflicts which cannot be resolved easily, it is possible to ask the team who caused the conflict to solve it since all history is preserved. Then this team con clone the integration repository and merge it with its working repository. They can ask the person in charge to pull the changes back again.
